Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-30 paper/zhang-cook-laa-langrene-menendez.tex
section monotonicity

The goal of continuous optimisation is to find the best solution within
the space of all feasible solutions where typically the best solution is
decided by an objective function. Broadly speaking, optimization can be
unconstrained or constrained \citep{kelley1999iterative}. The
unconstrained problem can be formulated as a minimization (or
maximization) problem such as \(\min_{x} f(x)\) where
\(f:\mathbb{R}^n \rightarrow \mathbb{R}\) is an objective function with
certain properties defined in an \(L^p\) space. In this case, solutions
rely on gradient descent or ascent methods. In the constrained
optimization problem additional restrictions are introduced via a set of
functions that can be convex or non-convex:
\(g_i:\mathbb{R}^n \rightarrow \mathbb{R}\) for \(i = 1, \ldots k\) and
hence the problem can be written as \(\min_{x} f(x)\) \emph{subject to}
\(g_i(x) \leq 0\). Here methods such as Langrange multipliers and convex
optimization methods including linear and quadratic programming can be
used.

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=0.5\linewidth,height=0.25\textheight]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/img/tour_path}

}

\caption[Each square (frame) represents the projected data with a corresponding basis]{Each square (frame) represents the projected data with a corresponding basis. Blue frames are found by an optimisation algorithm iteratively whilst the white frames are constructed between two blue frames by geodesic interpolation.}\label{fig:tour-path}
\end{figure}
\end{Schunk}

@@

A starting point of diagnosing an optimiser is to understand how many
search the optimiser has conducted. One may want to simply plot the
index value of the search points across its natural order. A point
geometry may work well if each iteration has a similar number of points,
however, the plot will be disproportionate if some iterations have
considerably more points than other - it over-emphasizes the iterations
that have more search points! An alternative is to summarise the search
in each iteration using boxplot where each iteration will be spaced out
equally. Occasionally, one may still want to switch back to point
geometry if the number of points is small and this can be achieved via
the \texttt{cutoff} argument. Additional annotation can be added with
new layers, for example, the number of points searched in each iteration
can be added as text label at the bottom of each iteration; the anchor
bases to interpolate are connected and highlighted in a larger size; and
the color of the last iteration is in a grey scale to indicate no better
basis found in this iteration.

@@

\begin{Schunk}
\begin{widefigure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-search-1}

}

\caption[A comparison of search by two otimisers]{A comparison of search by two otimisers: SA (left) and SAJO (right) on a 2D projection of a six-variable dataset, \code{boa6}, using the holes index. Both optimisers find the final basis with similar index value while it takes SAJO more iteration because the algorithm allows a probabilistic acceptance of bases with lower index value, as observed in iteration 4 and 6-8.}\label{fig:toy-search}
\end{widefigure}
\end{Schunk}

@@

\begin{Schunk}
\begin{widefigure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-interp-1}

}

\caption[Trace plots of the interpolating bases with the same optimisation routine as the previous figure]{Trace plots of the interpolating bases with the same optimisation routine as the previous figure. Both traces are smooth while the change of index value in each iteration may not be monotinic.}\label{fig:toy-interp}
\end{widefigure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-pca-1}

}

\caption[The PCA plot of 1D projection problem on the 5-variable dataset, \code{boa5}, using the holes indexwith two optimisers]{The PCA plot of 1D projection problem on the 5-variable dataset, \code{boa5}, using the holes indexwith two optimisers: SA and PD. All the bases in PD has been flipped and a grey dashed line has been annotated to indicate the symmetry of two starting bases.}\label{fig:toy-pca}
\end{figure}
\end{Schunk}

Apart from checking the progression of an optimiser, looking at how the
points evaluated by the optimisers look like in the space is another
interest. Given the orthonormality constraint, the space of projection
bases \(\mathbf{A}_{p \times d}\) is a \(p \times d\) dimension sphere
and dimension reduction methods, i.e.~principal component analysis is
applied first to project all the bases onto a 2D space. In a projection
pursuit guided tour optimisation, there are various type of bases
involved: 1) The start basis; 2) The anchor bases that have the highest
index value in each iteration; 3) The search bases that an optimiser
evaluated to produce the anchor bases; 4) The interpolating bases on the
interpolation path; and finally 5) the end basis. The importance of
these basis differs with the most important ones being the start,
interpolating and end bases. Anchor and search bases can be turned on
with argument \texttt{details\ =\ TRUE}. Sometimes, two optimisers can
start with the same basis but finish with bases of opposite sign. This
happens because the projection is invariate to the sign difference of
the bases and so does the index value, however, this creates
difficulties for comparing end bases. A flip sign device is implemented
to flip the sign of all the bases in one optimisation if the situation
described above happens and to ensure different routines finish close to
each other.

Several annotations have been made to help understanding this plot. The
original space of the bases is a high dimensional sphere and random
bases on the sphere can be generated via the CRAN package
\CRANpkg{geozoo} \citep{geozoo}. Along with the bases recorded during
the optimisation and a zero basis, PCA is performed to get the first two
PC coordinates of all the bases. The search space in the 2D space is a
circle with the origin being the PC coordinates of the zero matrix, and
radius estimated as the largest distance between the origin and all the
bases. The theoretical best basis is known with simulated data and can
be labelled for comparing the how close the ending basis to the
theoretical one for different optimisers. Various aesthetics, i.e.~size,
alpha and color, are applicable to emphasize the crucial elements and
adjust for the presentation. For example, anchor points and search
points are less important and a smaller size and alpha is used; The
interpolation paths are more informative if alpha increases from start
to finish (that is, the path is more opaque towards the end).

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-pca-animated-1}

}

\caption{Six selected frames from the animated PCA plots in the previous figure. With animation, the start and end position of each optimisation is easier to identify.  A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

Animation is another display to show how the search porgresses from
start to finish in the space and an \texttt{animate\ =\ TRUE} argument
is used to enable the animation. Figure \ref{fig:toy-pca-animated} shows
six frames from the animation of the PCA plot in Figure
\ref{fig:toy-pca}. An additional piece of information one can learn from
this animation is that the SA search finds its end basis quicker than
the PD search since SA has finished in the 5th frame while PD is still
making more progression.

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-tour-1}

}

\caption{Six selected frames from the tour animation for viewing the same two optmisations as previous two figures. The tour animation allows for an appreciation of the search bases in the original high dimensional space. A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504328122/9be84db563}}\label{fig:toy-tour}
\end{figure}
\end{Schunk}

@@

@@

Random variables with different distributions have been simulated and
the distributional form of each variable is presented in Equations
\ref{eq:sim-norm} to \ref{eq:sim-x7}. Variable \texttt{x1}, \texttt{x8},
\texttt{x9} and \texttt{x10} are normal noise with zero mean and unit
variance and \texttt{x2} to \texttt{x7} are normal mixtures with varied
weights and locations. All the variables have been scaled to have an
overall unit variance before running the projection pursuit.

@@

A non-monotonic interpolation path has already been given in Figure
\ref{fig:toy-interp}: to get to the target basis from the current one,
the interpolator may have passed a basis with even higher index value.
This motivates the design of an interruption to check whether higher
index value can be reached during the interpolation. If such a basis can
be found, the optimiser will start the next iteration from that basis
instead of the target one. Figure \ref{fig:interruption} contrasts the
trace with and without the interruption for the simulated annealing
optimiser and it can be observed that while the first two interpolation
are identical, a better basis has been found than the target one in the
third interpolation. Rather than starting the next iteration from the
``target basis'' on Time 62, as shown in the left panel, the
interruption, on the right panel, starts the next iteration from the
``interpolation basis'' on Time 61. The interruption has also detected
better basis on the fourth interpolation. With the interruption, the
optimiser is able to find the final basis with a higher index value
(0.865 vs.~0.879).

\begin{Schunk}
\begin{widefigure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/interruption-1}

}

\caption[Trace plot of 2D projection on \code{boa6} data with holes index optimised by optimiser SA]{Trace plot of 2D projection on \code{boa6} data with holes index optimised by optimiser SA. The purpose of the plot is to compare the effect of implementing the interruption that avoid fully interpolating to the target basis if a better one can be found during the interpolation. With this implementation, the optimiser is able to find a better final basis.}\label{fig:interruption}
\end{widefigure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/polish-1}

}

\caption[Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative]{Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative. The left panel shows the final projected data before polish and the right panel shows the one after. The separation of the clusters on the y axis becomes sharper after the polish. }\label{fig:polish}
\end{figure}
\end{Schunk}

@@

\hypertarget{fliping-the-sign-in-the-bases}{%
\subsection{fliping the sign in the
bases}\label{fliping-the-sign-in-the-bases}}

@@

\begin{Schunk}
\begin{widefigure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/noisy-better-geo-1}

}

\caption[1D projection on 5\-variable dataset \code{boa5} with \code{norm\_kol} index]{1D projection on 5\-variable dataset \code{boa5} with \code{norm\_kol} index. The trace plot shows the failure of pseudo derivative on non-smooth index. The PCA plot also shows that simulated annealing is searching the area close to the theoretical best while pseudo derivative can't couple with the non-continuity in the index.}\label{fig:noisy-better-geo}
\end{widefigure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/kol-result-1}

}

\caption[1D projection of data \code{boa6} on \code{norm\_kol} index,  optimised by SA and SAJO]{1D projection of data \code{boa6} on \code{norm\_kol} index,  optimised by SA and SAJO. Two different neighbourhood size of 0.5 and 0.7 is used. The finish point of each path is larger than the start point and optimums are separately labelled with * representing the global optimum and x the local optimum The color of the path is based on whether the optimiser finds the global or local optimum, after polishing.}\label{fig:kol-result}
\end{figure}
\end{Schunk}

@@

  \begin{itemize}
  \tightlist
  \item
    \code{get\_best()} extracts the best basis found in the data object
  \item
    \code{get\_start()} extracts the starting basis
  \item
    \code{get\_interp()} extracts the observations in the interpolation
  \item
    \code{get\_interp\_last()} extracts the end observations of the
    interpolation in each iteration
  \item
    \code{get\_anchor()} extracts the target observations found by the
    optimiser
  \item
    \code{get\_search()} extracts the search observations evaluated by
    the optimiser
  \item
    \code{get\_search\_count()} produces the summary table of the number
    of observation in each iteration
  \item
    \code{get\_center()} produces the center point of the basis space
    estimated by the starting points
  \item
    \code{get\_space\_param()} produces the coordinates of the center
    and radius of the basis space
  \item
    \code{get\_theo()} extracts the theoretical observations from the
    data object
  \item
    \code{get\_interrupt()} extract the end point of the interpolation
    and the target point when an interruption happens
  \item
    \code{get\_basis\_matrix()}: flattens all the bases into a matrix
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

@@

  \begin{itemize}
  \tightlist
  \item
    \code{add\_*()} are internal wrapper functions that facilitate the
    composition of PCA plot
  \item
    \code{theme\_fern()} and \code{format\_label()} for better display
    of the grid lines and axis formatting
  \item
    \code{clean\_method()} for clean up the name of the optimisers
  \item
    \code{botanical\_palettes} is a collection of color palettes from
    Australian native plants. Quantitative palettes include daisy,
    banksia and cherry and sequential palettes contain fern and acacia.
  \item
    \code{botanical\_pal()} as the color interpolator
  \item
    \code{scale\_color\_botanical()} is a ggplot2 scale for botanical
    palettes.
  \end{itemize}
\end{itemize}

>>>>

The goal of continuous optimisation is to find the best solution within
the space of all feasible solutions where typically the best solution is
decided by an objective function. Broadly speaking, optimization can be
unconstrained or constrained \citep{kelley1999iterative}. The
unconstrained problem can be formulated as a minimization (or
maximization) problem such as \(\min_{x} f(x)\) where
\(f:\mathbb{R}^n \rightarrow \mathbb{R}\) is an objective function with
certain properties defined in an \(L^p\) space. In this case, solutions
rely on gradient descent or ascent methods. In the constrained
optimization problem additional restrictions are introduced via a set of
functions that can be convex or non-convex:
\(g_i:\mathbb{R}^n \rightarrow \mathbb{R}\) for \(i = 1, \ldots k\) and
hence the problem can be written as \(\min_{x} f(x)\) \emph{subject to}
\(g_i(x) \leq 0\). Here methods such as multipliers and convex
optimization methods including linear and quadratic programming can be
used.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=0.5\linewidth,height=0.25\textheight]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/img/tour_path} \caption[Each square (frame) represents the projected data with a corresponding basis]{Each square (frame) represents the projected data with a corresponding basis. Blue frames are found by an optimisation algorithm iteratively whilst the white frames are constructed between two blue frames by geodesic interpolation.}\label{fig:tour-path}
\end{figure}
\end{Schunk}

@@

A starting point of diagnosing an optimiser is to understand how many
search the optimiser has conducted. One may want to simply plot the
index value of the search points across its natural order. A point
geometry may work well if each iteration has a similar number of points,
however, the plot will be disproportionate if some iterations have
considerably more points than other - it over-emphasizes the iterations
that have more search points! An alternative is to summarise the search
in each iteration using boxplot where each iteration will be spaced out
equally. Occasionally, one may still want to switch back to point
geometry if the number of points is small and this can be achieved via
the \texttt{cutoff} argument. Additional annotation can be added with
new layers, for example, the number of points searched in each iteration
can be added as text label at the bottom of each iteration; the anchor
bases to interpolate are connected and highlighted in a larger size; and
the colour of the last iteration is in a grey scale to indicate no
better basis found in this iteration.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-search-1} \caption[A comparison of search by two otimisers]{A comparison of search by two otimisers: SA (left) and SAJO (right) on a 2D projection of a six-variable dataset, \code{boa6}, using the holes index. Both optimisers find the final basis with similar index value while it takes SAJO more iteration because the algorithm allows a probabilistic acceptance of bases with lower index value, as observed in iteration 4 and 6-8.}\label{fig:toy-search}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-interp-1} \caption[Trace plots of the interpolating bases with the same optimisation routine as the previous figure]{Trace plots of the interpolating bases with the same optimisation routine as the previous figure. Both traces are smooth while the change of index value in each iteration may not be monotinic.}\label{fig:toy-interp}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-pca-1} \caption[The PCA plot of 1D projection problem on the 5-variable dataset, \code{boa5}, using the holes indexwith two optimisers]{The PCA plot of 1D projection problem on the 5-variable dataset, \code{boa5}, using the holes indexwith two optimisers: SA and PD. All the bases in PD has been flipped and a grey dashed line has been annotated to indicate the symmetry of two starting bases.}\label{fig:toy-pca}
\end{figure}
\end{Schunk}

Apart from checking the progression of an optimiser, looking at how the
points evaluated by the optimisers look like in the space is another
interest. Given the orthonormality constraint, the space of projection
bases \(\mathbf{A}_{p \times d}\) is a \(p \times d\) dimension sphere
and dimension reduction methods, i.e.~principal component analysis is
applied first to project all the bases onto a 2D space. In a projection
pursuit guided tour optimisation, there are various type of bases
involved: 1) The start basis; 2) The anchor bases that have the highest
index value in each iteration; 3) The search bases that an optimiser
evaluated to produce the anchor bases; 4) The interpolating bases on the
interpolation path; and finally 5) the end basis. The importance of
these basis differs with the most important ones being the start,
interpolating and end bases. Anchor and search bases can be turned on
with argument \texttt{details\ =\ TRUE}. Sometimes, two optimisers can
start with the same basis but finish with bases of opposite sign. This
happens because the projection is invariant to the sign difference of
the bases and so does the index value, however, this creates
difficulties for comparing end bases. A flip sign device is implemented
to flip the sign of all the bases in one optimisation if the situation
described above happens and to ensure different routines finish close to
each other.

Several annotations have been made to help understanding this plot. The
original space of the bases is a high dimensional sphere and random
bases on the sphere can be generated via the CRAN package
\CRANpkg{geozoo} \citep{geozoo}. Along with the bases recorded during
the optimisation and a zero basis, PCA is performed to get the first two
PC coordinates of all the bases. The search space in the 2D space is a
circle with the origin being the PC coordinates of the zero matrix, and
radius estimated as the largest distance between the origin and all the
bases. The theoretical best basis is known with simulated data and can
be labelled for comparing the how close the ending basis to the
theoretical one for different optimisers. Various aesthetics, i.e.~size,
alpha and colour, are applicable to emphasize the crucial elements and
adjust for the presentation. For example, anchor points and search
points are less important and a smaller size and alpha is used; The
interpolation paths are more informative if alpha increases from start
to finish (that is, the path is more opaque towards the end).

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-pca-animated-1} \caption{Six selected frames from the animated PCA plots in the previous figure. With animation, the start and end position of each optimisation is easier to identify.  A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504242845/b73f37175a}}\label{fig:toy-pca-animated}
\end{figure}
\end{Schunk}

Animation is another display to show how the search progresses from
start to finish in the space and an \texttt{animate\ =\ TRUE} argument
is used to enable the animation. Figure \ref{fig:toy-pca-animated} shows
six frames from the animation of the PCA plot in Figure
\ref{fig:toy-pca}. An additional piece of information one can learn from
this animation is that the SA search finds its end basis quicker than
the PD search since SA has finished in the 5th frame while PD is still
making more progression.

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/toy-tour-1} \caption{Six selected frames from the tour animation for viewing the same two optmisations as previous two figures. The tour animation allows for an appreciation of the search bases in the original high dimensional space. A full video of this aimation can be found at \url{https://vimeo.com/user132007430/review/504328122/9be84db563}}\label{fig:toy-tour}
\end{figure}
\end{Schunk}

@@

Something to fill here \ldots{}

@@

Random variables with different distributions have been simulated and
the distributional form of each variable is presented in Equations
\ref{eq:sim-norm} to \ref{eq:sim-x7}. Variable \texttt{x1}, \texttt{x8},
\texttt{x9} and \texttt{x10} are normal noise with zero mean and unit
variance, and \texttt{x2} to \texttt{x7} are normal mixtures with varied
weights and locations. All the variables have been scaled to have an
overall unit variance before projection pursuit.

@@

An example of non-monotonic interpolation has been given in Figure
\ref{fig:toy-interp}: a path that passes bases with higher index value
than the target one. With optimiser SAJO, a non-monotonic interpolation
is justified since the target bases do not necessarily have a higher
index value than the current one, while this is not the case for SA. The
original trace plot for a 2D projection, optimised by SA, is shown on
the left panel of Figure \ref{fig:interruption} and one can observe
clearly that the non-monotonic interpolation has undermined the
optimiser to realise its full potential. Hence, an interruption is
implemented to stop the interpolation at the basis with the highest
index value. The right panel of Figure \ref{fig:interruption} presents
the trace plot after implementing such interruption and it can be
observed that while the first two interpolations are identical, in the
third interpolation the basis at time 61 has a higher index value than
the target. Rather than starting the next iteration from the target
basis on Time 65 as shown in the left panel, the optimiser, on the right
panel, starts the next iteration from the interpolation basis on Time
61. With the interruption, the optimiser is able to find the final basis
with a index value higher than the most promising basis when the
interruption is not implemented.

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/interruption-1} \caption[Trace plot of 2D projection on \code{boa6} data with holes index, optimised by optimiser SA]{Trace plot of 2D projection on \code{boa6} data with holes index, optimised by optimiser SA.}\label{fig:interruption}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/polish-1} \caption[Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative]{Two-D projection on \code{boa6} data with holes index optimised by pseudo derivative. The left panel shows the final projected data before polish and the right panel shows the one after. The separation of the clusters on the y axis becomes sharper after the polish. }\label{fig:polish}
\end{figure}
\end{Schunk}

@@

\hypertarget{flipping-the-sign-in-the-bases}{%
\subsection{Flipping the sign in the
bases}\label{flipping-the-sign-in-the-bases}}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/noisy-better-geo-1} \caption[1D projection on 5\-variable dataset \code{boa5} with \code{norm\_kol} index]{1D projection on 5\-variable dataset \code{boa5} with \code{norm\_kol} index. The trace plot shows the failure of pseudo derivative on non-smooth index. The PCA plot also shows that simulated annealing is searching the area close to the theoretical best while pseudo derivative can't couple with the non-continuity in the index.}\label{fig:noisy-better-geo}
\end{figure}
\end{Schunk}

@@

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/kol-result-1} \caption[1D projection of data \code{boa6} on \code{norm\_kol} index,  optimised by SA and SAJO]{1D projection of data \code{boa6} on \code{norm\_kol} index,  optimised by SA and SAJO. Two different neighbourhood size of 0.5 and 0.7 is used. The finish point of each path is larger than the start point and optimums are separately labelled with * representing the global optimum and x the local optimum The colour of the path is based on whether the optimiser finds the global or local optimum, after polishing.}\label{fig:kol-result}
\end{figure}
\end{Schunk}

@@

  \begin{itemize}
  \tightlist
  \item
    \code{get\_best()} extracts the best basis found in the data object
  \item
    \code{get\_start()} extracts the starting basis
  \item
    \code{get\_interp()} extracts the observations in the interpolation
  \item
    \code{get\_interp\_last()} extracts the end observations of the
    interpolation in each iteration
  \item
    \code{get\_anchor()} extracts the target observations found by the
    optimiser
  \item
    \code{get\_search()} extracts the search observations evaluated by
    the optimiser
  \item
    \code{get\_search\_count()} produces the summary table of the number
    of observation in each iteration
  \item
    \code{get\_centre()} produces the centre point of the basis space
    estimated by the starting points
  \item
    \code{get\_space\_param()} produces the coordinates of the centre
    and radius of the basis space
  \item
    \code{get\_theo()} extracts the theoretical observations from the
    data object
  \item
    \code{get\_interrupt()} extract the end point of the interpolation
    and the target point when an interruption happens
  \item
    \code{get\_basis\_matrix()}: flattens all the bases into a matrix
  \end{itemize}
\item
  \code{bind\_*()} incorporates additional information outside the tour
  optimisation into the data object.

@@

  \begin{itemize}
  \tightlist
  \item
    \code{add\_*()} are internal wrapper functions that facilitate the
    composition of PCA plot
  \item
    \code{theme\_fern()} and \code{format\_label()} for better display
    of the grid lines and axis formatting
  \item
    \code{clean\_method()} for clean up the name of the optimisers
  \item
    \code{botanical\_palettes} is a collection of colour palettes from
    Australian native plants. Quantitative palettes include daisy,
    banksia and cherry and sequential palettes contain fern and acacia.
  \item
    \code{botanical\_pal()} as the colour interpolator
  \end{itemize}
\end{itemize}
